On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-04 tt_intro.tex
Commit before going to bed
Since I don't feel well, let me go to bed now.

The behavior of an oritatami system at delay 1 can be described by a sequence of $S$ of $b$ (bound), $t_s$ (straight tunnel section), $t_o$ (obtuse-turn tunnel section), and $t_a$ (acute-turn tunnel section); priority is given to tunnel, that is, $S[i]$ is $t_s$ (resp.~$t_o$, $t_a$) if the $i$-th bead of the system is stabilized not only by being bonded but also through a straight (resp. obtuse-turn, acute-turn) tunnel section. 
Let us introduce $t$ as a wildcard for $t_s$, $t_o$, and $t_a$. 
We also let $S$ take the value $\blacksquare$ for halt (due to the lack of free neighbors). 
A tunnel is a set of

@@

We now prove that in ``almost all'' tunnels is a troll domiciled and robs the transcript of binding capability (the original story is from \cite{Pratchett1992}). 
Originally, we tried to find a troll in every tunnel but failed; a troll seems to dislike the very first bead $w[1]$, or its property that only $\alpha$+1 beads around may take all hands of $w[1]$ thanks to the absence of its predecessor; any other bead must be surrounded by at least $\alpha+2$ beads in order to be free from free hand because a bead cannot bind with its predecessor or successor. 
We call the bead $w[1]$ \textit{singular}. 
A tunnel is \textit{singular} if its entrance or exit is next to $w[1]$. 
There can be at most 3 tunnels around one bead so that no more than 3 tunnels can be singular. 
A singular tunnel will be denoted with the superscript $\times$ like $t_s^\times$ or $t^\times$. 
In contrast, the notation without $\times$ such as $t_s$ and $t$ shall imply their non-singularity.

>>>>

The behavior of an oritatami system at delay 1 can be described by a sequence of $S$ of $b$ (bound), $t_s$ (straight tunnel section), $t_o$ (obtuse-turn tunnel section), and $t_a$ (acute-turn tunnel section); priority is given to tunnel, that is, $S[i]$ is $t_s$ (resp.~$t_o$, $t_a$) if the $i$-th bead of the system is stabilized not only by being bonded but also through a straight (resp. obtuse-turn, acute-turn) tunnel section. 
Let us introduce $t$ as a wildcard for $t_s$, $t_o$, and $t_a$. 
We also let $S$ take the value $\blacksquare$ for halt (due to the lack of free neighbors).

@@

We now prove that in ``almost all'' tunnels is a troll domiciled and robs the transcript of binding capability (the original story is from \cite{Pratchett1992}). 
Originally, we tried to find a troll in every tunnel but failed; a troll seems to dislike the very first bead $w[1]$, or its property that only $\alpha$+1 beads around may take all hands of $w[1]$ thanks to the absence of its predecessor; any other bead must be surrounded by at least $\alpha+2$ beads in order to be free from free hand because a bead cannot bind with its predecessor or successor. 
We call a bead \textit{singular} if it is surrounded by only $\alpha+1$ beads but forms $\alpha$ bonds. 
Any bead but $w[1]$ can be singular because of their predecessor and successor. 
A tunnel is \textit{singular} if its entrance or exit is next to $w[1]$ that is singular. 
There can be at most 3 tunnels around one bead so that no more than 3 tunnels can be singular. 
A singular tunnel will be denoted with the superscript $\times$ like $t_s^\times$ or $t^\times$. 
In contrast, the notation without $\times$ such as $t_s$ and $t$ shall imply their non-singularity.
